Biofouling

### 2023-06-12 smelt_2019_allseasons/Zoop 2019.Rmd
exporting final dataframe to data_clean folder
update where data gets exported for biofouling rmd

#remove throw samples
winter <- winter[!(winter$Method=="Throw"),]
#change ostracod taxa
winter[winter$Taxon %in% c("Ostracods"),]$Taxa <- "Ostracod"
#merge with catch df
#condense to columns of interest
winter2 <- winter %>%
  rename(ID = Taxon) %>%
  select(Location, Date, Taxa, samplecount, ind_m3, bio_m3, Day, Month, MD) %>%
  group_by(Location, Date, Taxa, Day, Month, MD) %>%
  summarize(ind_m3 = sum(ind_m3), bio_m3 = sum(bio_m3))

@@

#remove 0's
caught.19 <- all2019[!(all2019$ind_m3==0),]
```

>>>>

#remove throw samples
winter <- winter[!(winter$Method=="Throw"),]
#change ostracod taxa
winter[winter$Taxon %in% c("Ostracods"),]$Taxa <- "Ostracod"
#merge with catch df

#condense to columns of interest
winter2 <- winter %>%
  rename(ID = Taxon) %>%
  select(Location, Date, Taxa, samplecount, ind_m3, bio_m3, Day, Month, MD) %>%
  group_by(Location, Date, Taxa, Day, Month, MD) %>%
  summarize(ind_m3 = sum(ind_m3), bio_m3 = sum(bio_m3))

@@

#remove 0's
caught.19 <- all2019[!(all2019$ind_m3==0),]

#write file for biofouling comparison
write.csv(caught.19, "smelt_2019_allseasons/data_clean/Zoop.catch.csv", row.names=FALSE)
```
